Models, derivatives, response diversity

### 2024-07-05 models_derivatives_response_diversity.Rmd
lepomis run with zip

no_exclusion_predictions_all <- list.files(path = "total_models/predictions/temp", pattern = ".rds", full.names = TRUE) |>
  map_dfr(readRDS)

# save total predictions as RDS
saveRDS(no_exclusion_predictions_all, "total_models/df_pred_all.rds")

@@

>>>>

simplified_predictions_all <- list.files(path = "total_models/predictions/temp", pattern = ".rds", full.names = TRUE) |>
  map_dfr(readRDS)

# save total predictions as RDS
saveRDS(simplified_predictions_all, "total_models/df_pred_all.rds")

@@

```{r}
# check out lepomis gibbosus
excl_model_predictions <- readRDS("total_models/df_pred_no_exclusion.rds")
excl_model_predictions |> 
  filter(species == "Lepomis_gibbosus") |> 
    ggplot(aes(temp, fit)) +
  # geom_ribbon(aes(ymin = (fit - se.fit), ymax = (fit + se.fit), fill = factor(species)), alpha = 0.3) +
  geom_line(aes(color = factor(species))) +
  theme_bw() +
  facet_wrap(~species, scale = "free_y", labeller = labeller(species = label_wrap_gen(width = 10))) +
  theme(strip.background = element_rect(fill = "lightgrey"), strip.text = element_text(size = 6)) +
  scale_color_viridis(discrete = TRUE, guide = NULL, option = "G", aesthetics = c("color", "fill")) +
  xlab("Temperature") +
  ylab("Abundance")
```
